Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-03-23 documents/cpm.tex
changes to Hogg's comments

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science ---
the most precise photometric measurements of stars ever made ---
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level; So that
it can capture more fine-grained information about the variation of the spacecraft.
The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star. In addition, we use the target star’s future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, we ensure that information about any transit will be perfectly isolated from the model. 
The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components), which we set by cross-validation. 
We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
We find that we can consistently outperform (for the purposes of exoplanet detection) the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.

@@

From the point of view of the present paper, one can only guarantee that {\em no} stellar variability is removed if the stars do not depend on time at all. If both the target star signal as well as some of the other stars do depend on time, then time acts as a confounder influencing both, and thus the true signals are not statistically independent, and thus the target signal may be compromised. We suspect that this effect is limited in \cite{pdc2,pdc3} since only eight principal components are used, which limits the capacity of the model.

@@

The first general idea about data-driven modeling of the kind used here
  is that each data point or data source is going to be 
  \emph{predicted} with or using a parameterized mathematical function of \emph{other data}.
That is, given a choice of some \emph{target} \Kepler\ data,
  we are going to find parameters of a function that takes as input some of the other \Kepler\ data,
  and provides as output predictions of the target data.
The simplest models are \emph{linear models},
  in which predictions for the target data are built from linear combinations of the other data,
  and in which the objective functions are quadratic in the prediction residual.
Examples of quadratic objective functions include Gaussian likelihoods, mean-squared-error, and chi-square statistics.
These models are simple,
  not just because they are easy to express and compute,
  but because optimization is convex:
There is only one optimum for the objective function.

@@

\begin{figure}[htb]
\centering
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5088536-5}
\caption{}
\end{subfigure}%
\hfill
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5949551-5}
\caption{}
\end{subfigure}
\caption{\label{ccd} Stars on the same CCD share systematic errors. 
The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; 
here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
but far enough apart such that there is no stray light from one affecting the other. 
Each panel shows the pixels contributing to the respective star. 
Note that there exist similar trends in these two stars, caused by systematic errors. 
%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\columnwidth]{train_and_test}
\caption{\label{train-and-test} Train-and-test framework. Data near the target point $t_{n}$ within $\Delta t$ is excluded in the training set}
\end{figure}

In addition to the pixel set $m'\in\set{M}_m$ from other stars,  
  we also include the past and future of the target star --- autoregressive (AR) component as input 
  to remove more of the stellar variability and thus increase the sensitivity for transits. 
To do this, we select an exclusion window of half-width $\Delta t$ including R data points, 
  where $\Delta t\sim 10$\, h (as big as the window in the train-and-test framework) 
  around the point of time $t_{n}$ being corrected, 
  to ensure that we do not remove the transit itself 
  and then use $S$ closest future and past time points subject to that exclusion. 
That is, for every pixel $m$ in the target star , we construct $S$ virtual time series, 
  in which every component $v$ is defined to be     
\begin{eqnarray}
I_{v,n} = I_{m,n-R-k}\ or\ I_{v,n} = I_{m,n+R+k},
\quad,
\end{eqnarray}
where $k = 1, 2\dots, S,$ so if there are totally $M$ pixels in the target stars, 
  we will finally add $2\cdot M\cdot S$\Bernhard{not quite: if I am right, then there are overall $(2R-1)$ in the exclusion zone, and $2S+2$ are used, for each pixel} \Dun{I changed k to be $1,2\dots, S$ so, so for every pixel, $2S$ are used} 
  autoregressive components into the predictors, which constructs the autoregressive set $\set{V}_m$

As mentioned above, in the context of this project,
  a model is something that can predict data given settings of some parameters,
  and an objective function that can be used to find best values for those parameters.
It is often preferable to work in a probabilistic mode in which the objective function can be justified
  in terms of a likelihood (probability for the data given the model)
  or a posterior probability density function (likelihood times a prior pdf).
The \name\ treats each \Kepler\ data point $I_{m,n}$ as being
  predictable from a linear combination of data points $I_{m',n}$,
  where $m'$ is from the set of non-overlapping pixels $m'\in\set{M}_m$.
\begin{eqnarray}
I_{m,n}         &=& I^{\ast}_{m,n} + e_{m,n}
\\
I^{\ast}_{m,n}  &=& \sum_{m'\in\set{M}_m} a_{m,n,m'}\,I_{m',n} + \sum_{v\in\set{V}_m} b_{m,n,v}\,I_{v,n}
\quad,
\end{eqnarray}
where $I^{\ast}_{m,n}$ is the prediction (by the model) for data point $I_{m,n}$,
  $e_{m,n}$ is a noise contribution or residual away from the prediction,
  and the $a_{m,n,m'}$ and $b_{m,n,k}$ are the parameters (linear coefficients of the prediction).
The parameters $a_{m,n,m'}$ and $b_{m,n,k}$ have indices $m$ because
  they are different for every pixel $m$,
  and they will even be different for every time step $n$;
  that is, there will be a separate best-fit value for the parameters for every $I_{m,n}$.
If we presume that the residuals away from the prediction are normally distributed with zero mean
  and known variance,
  likelihood optimization reduces to $\chi^2$ \Bernhard{maybe better $\chi^2$?} minimization.
We add to the standard chi-squared definition a regularization term
  (equivalent to multiplying the likelihood by a Gaussian prior pdf)
  that penalizes large absolute values for the the coefficients $a_{m,n,m'}$:
\begin{eqnarray}
\chi^2_{m,n}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{m,n'} - I^{\ast}_{m,n',n}]^2}{\sigma^2_{m,n'}}
                 + \lambda_{a}\sum_{m'\in\set{M}_m}a_{m,n,m'}^2 + \lambda_{b}\sum_{v\in\set{V}_m}b_{m,n,v}^2
\\
I^{\ast}_{m,n',n} &=& \sum_{m'\in\set{M}_m} a_{m,n,m'}\,I_{m',n'} + \sum_{v\in\set{V}_m} b_{m,n,v}\,I_{v,n'}
\quad,
\end{eqnarray}
\Bernhard{(1) why does $I$ have three indices now, and what does that mean? In Eq. (3) there are only two indices. (2) do we need the sigmas at all, or could we absord this into the lambdas?}
\Dun{In CPM,  for every time points,  the $\chi^2$ minimization is independent, the third indice of $I^{\ast}$ indicates which time point is being optimized, I've added some words to explain it,  maybe we can find a better notation?}
where the $\sigma^2_{m,n'}$ are the (presumed known)\Bernhard{known, or estimated from data? 
  If not estimated, how do we know them?} individual-pixel noise variances, and $\lambda_{a}$, 
  $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{m,n,m'}, b_{m,n,v}$. 
  In general, $\lambda_a$ and $\lambda_b$ could depend on $m,n$, however, we do not make use of this freedom. 
  Here the prediction $I^{\ast}_{m,n',n}$ has three indices, because in \name\ the $\chi^2$ minimization for every time
  point is independent and the third indice--n indicates which time point the prediction $I^{\ast}_{m,n',n}$ is used for, 
  the detail of the independent $\chi^2$ minimization will be discussed as follows.

The train-and-test idea comes into the objective function $\chi^2_{m,n}$:
When we are computing the objective function $\chi^2_{m,n}$,
  we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
We train the model---that is, set the parameters $a_{m,n,m'}$ and $b_{m,n,v}$---%
  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{m,n}$.
Fortunately, given the form of the model,
  this minimization is just a linear solve (linear operation on the data).
Importantly however, and perhaps surprisingly, the objective function $\chi^2_{m,n}$ is \emph{different}
  for every target data point (pixel value to be predicted) $I_{m,n}$;
  we have to do an \emph{independent optimization} (or really linear solve)
  of the parameters for every pixel value we want to predict.
That is, every pixel datum $I_{m,n}$ we predict will have
  \emph{different} settings of the parameters $a_{m,n,m'}$ and $b_{m,n,v}$.
Since there are of order $10^{6}$ total pixel values in the \Kepler\ Target Pixel Files for \emph{each \Kepler\ target},
  and of order $10^7$ data sources used as basis functions in the linear fitting,
  this represents one fuck of a lot of linear solves,
  and a lot of parameters to obtain and record.

Once we have obtained the parameters $a_{m,n,m'}$ and $b_{m,n,v}$ corresponding to a particular data point $I_{m,n}$,
  we can make a \emph{prediction} $I^{\ast}_{m,n}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{m,n}$ itself,
  or even any of the pixel values that are nearby in angle or time
  (as described above).
  With all the predicted pixel values $I^{\ast}_{m,n}$ of the target star,  
  our new stellar flux estimates,
  what we will call the ``\name\ prediction'',
  is constructed from the \name\ pixels
  in precisely the same way as the official \Kepler\ SAP photometry
  is constructed from the Target Pixel Files.
That is, we perform a weighted sum of \name\ predicted pixels $I^{\ast}_{m,n}$ with weights $w_m$,
  all of which are either zero or unity,
  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
\begin{eqnarray}
S_n = \sum_m w_m\,I^{\ast}_{m,n}
\quad ,
\end{eqnarray}
where the sum is over the $M$ pixels that are associated with the target star and the weight $w_m$ is unity for pixels in the optimal
aperture while zero outside the optimal aperture.
 \Bernhard{if the sum is only over the pixels of the target star, then all $w_m$ are equal to 1 and they can be dropped}.
 \Dun{$w_m$ is 0 out of the optimal aperture,  we've added some words to explain it.}
As we have noted above and below, these photometric estimators are not optimal for any purpose,
  but improving them is beyond the scope of this project.

It is worth to mention that the \name\ prediction $S_{n}$ is constructed from predicted pixel value without any information about transits in the target star due to the train-and-test framework.\Bernhard{changed this --- I didn't understand it} \Dun{Does it look better now?} Therefore, it can be regarded as a light curve without transit signal. 
Based on this idea, 
  we can construct the ``\name\ flux'' (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved) to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray}
The \name\ flux is 
In some sense, it is this relative residual that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{compare_10187017}
\caption{\label{hyperparameter} Comparison between default and optimized hyper-parameters. 
In the top panel, SAP flux is plotted in black, \name\ prediction of default hyper parameters is in red line, 
\name\ prediction of optimized hyper-parameters is in green line. 
The middle panel shows the \name\ flux of the optimized hyper-parameters, 
while \name\ flux of the default hyper-parameters is in the bottom panel, 
the two vertical blue lines indicate the location of the transit signal, and signal to noise ratio is calculated in both situation. 
The optimized hyper-parameter performs better than the default one, but the results from both situation are close.}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{distortion_9822284_normal}
\caption{\label{distortion} \name\ preserves transit signals. 
Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284. 
In the top panel, the black points shows the SAP flux of the pixel with the injected signal, 
the green line is the fitting of the SAP flux, and the red line is the \name\ prediction. 
In the bottom panel, red and green points represent the \name\ flux and fit flux, 
while the signal value is indicated by the horizontal line. 
\name\ largely preserves the signal while the fitting flux overfit the signal.}
\end{figure}

@@

\caption{\label{fluxes} Corrected fluxes using \name, for 12 example stars, spanning the main magnitude (brightness) range encountered. 
In first column plots,   we consider bright stars with magnitude from 9 to 10.5, second cloumn are stars with magnitude from 11 to 12.5,  
and the third column are faint stars with magnitude above 13. In the first two rows, we present some quiet stars. 
In all three panels, the top panel shows the SAP flux (black) and the \name\ regression (red), i.e., our prediction of the star from other stars. 
The middle panel shows the \name\ flux corrected using the regression, and the bottom shows the PDC flux. 
One can see that the \name\ flux curve preserves the exoplanet transits (little downward spikes), 
while removing a substantial part of the variability present in the PDC flux. 
Both the bottom two rows present some variable stars with slow and fast variability. 
For the variable stars, we did not present the PDC comparison, since the PDC flux try to preserve intrinsic steller variability.}
\end{figure}

\begin{figure*}[htb]
\centering
\begin{subfigure}[htb]{0.33\columnwidth}
\includegraphics[width=\columnwidth]{pdc_cdpp12_r}
\caption{}
\end{subfigure}%
%\hfill
\begin{subfigure}[htb]{0.33\columnwidth}
\includegraphics[width=\columnwidth]{boxplot_r}
\caption{}
\end{subfigure}%
%\hfill
\begin{subfigure}[htb]{0.33\columnwidth}
\includegraphics[width=\columnwidth]{pdc_cdpp12_hist_r100}
\caption{}
\end{subfigure}
\caption{\label{cdpp} Comparison of the proposed method (\name) to the \Kepler\ Pre-search Data Conditioning (PDC) method 
in terms of Combined Differential Photometric Precision (CDPP) (see text). 
Plot (a) shows our performance (red) vs.\ the PDC performance in a scatter plot, as a function of star magnitude 
(note that larger magnitude means fainter stars, and smaller values of CDPP indicate a higher quality as measured by CDPP.  
Plot (b) bins the same dataset and shows box plots within each bin, indicating median, top quartile and bottom quartile. 
The red box corresponds to \name, while the black box refers to PDC. Plot (c), finally, shows a histogram of CDPP values. 
Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, indicating that our method overall outperforms PDC, the Kepler ``gold standard.'' 
}
\end{figure*}

>>>>

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science ---
the most precise photometric measurements of stars ever made ---
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level; So that
it can capture more fine-grained information about the variation of the spacecraft.
The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star. In addition, we use the target star’s future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components), which we set by cross-validation. 
We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
We find that we can consistently outperform (for the purposes of exoplanet detection)% 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.

@@

From the point of view of the present paper, 
one can only guarantee that {\em no} stellar variability is removed if the stars do not depend on time at all. 
If both the target star signal as well as some of the other stars do depend on time, 
  then time acts as a confounder influencing both, and thus the true signals are not statistically independent, 
  and thus the target signal may be compromised. 
We suspect that this effect is limited in \cite{pdc2,pdc3}, 
  since only eight principal components are used, which limits the capacity of the model.

@@

The first general idea about data-driven modelling of the kind used here
  is that each data point or data source is going to be 
  \emph{predicted} with or using a parameterized mathematical function of \emph{other data}.
That is, given a choice of some \emph{target} \Kepler\ data,
  we are going to find parameters of a function that takes as input some of the other \Kepler\ data,
  and provides as output predictions of the target data.
The simplest models are \emph{linear models},
  in which predictions for the target data are built from linear combinations of the other data,
  and in which the objective functions are quadratic in the prediction residual.
Examples of quadratic objective functions include Gaussian likelihoods, mean-squared-error, and chi-square statistics.
These models are simple,
  not just because they are easy to express and compute,
  but because optimization is convex:
There is only one optimum for the objective function.

@@

\begin{figure}[htb]
\centering
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5088536-5}
\caption{}
\end{subfigure}%
\hfill
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5949551-5}
\caption{}
\end{subfigure}
\caption{
  \label{ccd} 
  Stars on the same CCD share systematic errors. 
  The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; 
  here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
  but far enough apart such that there is no stray light from one affecting the other. 
  Each panel shows the pixels contributing to the respective star.
  Note that there exist similar trends in these two stars, caused by systematic errors. 
%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=0.8\columnwidth]{train_and_test}
\caption{
  \label{train-and-test} 
  Train-and-test framework. 
  Data near the target point $t_{n}$ within $\Delta t$ is excluded in the training set}
\end{figure}

In addition to the pixel set $m'\in\set{M}_m$ from other stars,  
  we also include the past and future of the target star --- autoregressive (AR) component as input 
  to remove more of the stellar variability and thus increase the sensitivity for transits. 
To do this, we select an exclusion window of half-width $\Delta t$ including R data points, 
  where $\Delta t\sim 10$\, h (as big as the window in the train-and-test framework) 
  around the point of time $t_{n}$ being corrected, 
  to ensure that we do not remove the transit itself 
  and then use $S$ closest future and past time points subject to that exclusion. 
That is, for every pixel $m$ in the target star , we construct $S$ virtual time series, 
  in which every component $v$ is defined to be     
\begin{eqnarray}
I_{v,n} = I_{m,n-R-k}\ or\ I_{v,n} = I_{m,n+R+k},
\quad,
\end{eqnarray}
where $k = 1, 2\dots, S,$ so if there are totally $M$ pixels in the target stars, 
  we will finally add $2\cdot M\cdot S$
  autoregressive components into the predictors, which constructs the autoregressive set $\set{V}_m$

As mentioned above, in the context of this project,
  a model is something that can predict data given settings of some parameters,
  and an objective function that can be used to find best values for those parameters.
It is often preferable to work in a probabilistic mode in which the objective function can be justified
  in terms of a likelihood (probability for the data given the model)
  or a posterior probability density function (likelihood times a prior pdf).
The \name\ treats each \Kepler\ data point $I_{m,n}$ as being
  predictable from a linear combination of data points $I_{m',n}$,
  where $m'$ is from the set of non-overlapping pixels $m'\in\set{M}_m$.
\begin{eqnarray}
I_{m,n}         &=& I^{\ast}_{m,n} + e_{m,n}
\\
I^{\ast}_{m,n}  &=& \sum_{m'\in\set{M}_m} a_{m,n,m'}\,I_{m',n} + \sum_{v\in\set{V}_m} b_{m,n,v}\,I_{v,n}
\quad,
\end{eqnarray}
where $I^{\ast}_{m,n}$ is the prediction (by the model) for data point $I_{m,n}$,
  $e_{m,n}$ is a noise contribution or residual away from the prediction,
  and the $a_{m,n,m'}$ and $b_{m,n,k}$ are the parameters (linear coefficients of the prediction).
The parameters $a_{m,n,m'}$ and $b_{m,n,k}$ have indices $m$ because
  they are different for every pixel $m$,
  and they will even be different for every time step $n$;
  that is, there will be a separate best-fit value for the parameters for every $I_{m,n}$.
If we presume that the residuals away from the prediction are normally distributed with zero mean
  and known variance,
  likelihood optimization reduces to $\chi^2$ minimization.
We add to the standard chi-squared definition a regularization term
  (equivalent to multiplying the likelihood by a Gaussian prior pdf)
  that penalizes large absolute values for the the coefficients $a_{m,n,m'}$:
\begin{eqnarray}
\chi^2_{m,n}    &=& \sum_{n'\in\set{N}_n} \frac{[I_{m,n'} - I^{\ast}_{m,n',n}]^2}{\sigma^2_{m,n'}}
                 + \lambda_{a}\sum_{m'\in\set{M}_m}a_{m,n,m'}^2 + \lambda_{b}\sum_{v\in\set{V}_m}b_{m,n,v}^2
\\
I^{\ast}_{m,n',n} &=& \sum_{m'\in\set{M}_m} a_{m,n,m'}\,I_{m',n'} + \sum_{v\in\set{V}_m} b_{m,n,v}\,I_{v,n'}
\quad,
\end{eqnarray}

where the $\sigma^2_{m,n'}$ are the (presumed known)\Bernhard{known, or estimated from data? 
  If not estimated, how do we know them?} individual-pixel noise variances, and $\lambda_{a}$, 
  $\lambda_{b}$ set the strength of the regularization (or width of the prior pdf) for parameters $a_{m,n,m'}, b_{m,n,v}$. 
  In general, $\lambda_a$ and $\lambda_b$ could depend on $m,n$, however, we do not make use of this freedom. 
  Here the prediction $I^{\ast}_{m,n',n}$ has three indices, 
  because in \name\ the $\chi^2$ minimization for every time
  point is independent and the third index--$n$ indicates 
  which time point the prediction $I^{\ast}_{m,n',n}$ is being trained for, 
  the detail of the independent $\chi^2$ minimization will be discussed below.

The train-and-test idea comes into the objective function $\chi^2_{m,n}$:
When we are computing the objective function $\chi^2_{m,n}$,
  we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
We train the model---that is, set the parameters $a_{m,n,m'}$ and $b_{m,n,v}$---%
  by choosing the full set of parameters $a_{m,n,m'}$ and $b_{m,n,v}$% 
  that jointly minimize the objective function $\chi^2_{m,n}$.
Fortunately, given the form of the model,
  this minimization is just a linear solve (linear operation on the data).
Importantly however, and perhaps surprisingly, the objective function $\chi^2_{m,n}$ is \emph{different}
  for every target data point (pixel value to be predicted) $I_{m,n}$;
  we have to do an \emph{independent optimization} (or really linear solve)
  of the parameters for every pixel value we want to predict at every time.
That is, every pixel datum $I_{m,n}$ we predict will have
  \emph{different} settings of the parameters $a_{m,n,m'}$ and $b_{m,n,v}$.
Since there are of order $10^{6}$ total pixel values in the \Kepler\ Target Pixel Files for \emph{each \Kepler\ target},
  and of order $10^{3}$ data sources used as basis functions in the linear fitting,
  this represents a lot of linear solves, and of order $10^{9}$ parameters to obtain and record.

Once we have obtained the parameters $a_{m,n,m'}$ and $b_{m,n,v}$ corresponding to a particular data point $I_{m,n}$,
  we can make a \emph{prediction} $I^{\ast}_{m,n}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{m,n}$ itself,
  nor even any of the pixel values that are nearby in angle or time
  (as described above).
  With all the predicted pixel values $I^{\ast}_{m,n}$ of the target star,  
  our new stellar flux estimates,
  what we will call the ``\name\ prediction'',
  is constructed from the \name\ pixels
  in precisely the same way as the official \Kepler\ SAP photometry
  is constructed from the Target Pixel Files.
That is, we perform a weighted sum of \name\ predicted pixels $I^{\ast}_{m,n}$ with weights $w_m$,
  all of which are either zero or unity,
  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
\begin{eqnarray}
S_n = \sum_m w_m\,I^{\ast}_{m,n}
\quad ,
\end{eqnarray}
where the sum is over the $M$ pixels that are associated with the target star and the weight $w_m$ is unity for pixels in the optimal
aperture while zero outside the optimal aperture.
 \Bernhard{if the sum is only over the pixels of the target star, then all $w_m$ are equal to 1 and they can be dropped}.
 \Dun{$w_m$ is 0 out of the optimal aperture,  we've added some words to explain it.}
As we have noted above and below, these photometric estimators are not optimal for any purpose,
  but improving them is beyond the scope of this project.

It is worth to mention that the \name\ prediction $S_{n}$ is constructed from predicted pixel value 
  without any information about transits in the target star due to the train-and-test framework.
  \Bernhard{changed this --- I didn't understand it} \Dun{Does it look better now?} 
Therefore, it can be regarded as a light curve without transit signal. 
Based on this idea, 
  we can construct the ``\name\ flux''% 
  (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved)% 
  to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray}
The \name\ flux is 
In some sense, it is this relative residual that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{compare_10187017}
\caption{
  \label{hyperparameter} 
  Comparison between default and optimized hyper-parameters. 
  In the top panel, SAP flux is plotted in black, \name\ prediction of default hyper parameters is in red line, 
    \name\ prediction of optimized hyper-parameters is in green line. 
  The middle panel shows the \name\ flux of the optimized hyper-parameters, 
    while \name\ flux of the default hyper-parameters is in the bottom panel, 
    the two vertical blue lines indicate the location of the transit signal, 
    and signal to noise ratio is calculated in both situation. 
  The optimized hyper-parameter performs better than the default one, 
    but the results from both situation are close.}
\end{figure}

@@

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{distortion_9822284_normal}
\caption{
  \label{distortion} 
  \name\ preserves transit signals. 
  Fake signal with amplitude 1.0005 is inserted into the single pixel (1, 2) of star KIC 9822284. 
  In the top panel, the black points shows the SAP flux of the pixel with the injected signal, 
    the green line is the fitting of the SAP flux, and the red line is the \name\ prediction. 
  In the bottom panel, red and green points represent the \name\ flux and fit flux, 
    while the signal value is indicated by the horizontal line. 
  \name\ largely preserves the signal while the fitting flux overfit the signal.}
\end{figure}

@@

\caption{
  \label{fluxes} 
  Corrected fluxes using \name, for 12 example stars, 
    spanning the main magnitude (brightness) range encountered. 
  In first column plots, we consider bright stars with magnitude from 9 to 10.5, 
    second cloumn are stars with magnitude from 11 to 12.5,  
    and the third column are faint stars with magnitude above 13. 
  In the first two rows, we present some quiet stars. 
  In all three panels, the top panel shows the SAP flux (black) and the \name\ regression (red), 
    i.e., our prediction of the star from other stars. 
  The middle panel shows the \name\ flux corrected using the regression, and the bottom shows the PDC flux. 
  One can see that the \name\ flux curve preserves the exoplanet transits (little downward spikes), 
    while removing a substantial part of the variability present in the PDC flux. 
  Both the bottom two rows present some variable stars with slow and fast variability. 
  For the variable stars, we did not present the PDC comparison, 
    since the PDC flux try to preserve intrinsic steller variability.}
\end{figure}

\begin{figure*}[htb]
\centering
\begin{subfigure}[htb]{0.33\columnwidth}
\includegraphics[width=\columnwidth]{pdc_cdpp12_r}
\caption{}
\end{subfigure}%
%\hfill
\begin{subfigure}[htb]{0.33\columnwidth}
\includegraphics[width=\columnwidth]{boxplot_r}
\caption{}
\end{subfigure}%
%\hfill
\begin{subfigure}[htb]{0.33\columnwidth}
\includegraphics[width=\columnwidth]{pdc_cdpp12_hist_r100}
\caption{}
\end{subfigure}
\caption{
  \label{cdpp} 
  Comparison of the proposed method (\name) to the \Kepler\ Pre-search Data Conditioning (PDC) method 
    in terms of Combined Differential Photometric Precision (CDPP) (see text). 
  Plot (a) shows our performance (red) vs.\ the PDC performance in a scatter plot, as a function of star magnitude 
    (note that larger magnitude means fainter stars, 
    and smaller values of CDPP indicate a higher quality as measured by CDPP.  
  Plot (b) bins the same dataset and shows box plots within each bin, 
    indicating median, top quartile and bottom quartile. 
  The red box corresponds to \name, while the black box refers to PDC. 
  Plot (c), finally, shows a histogram of CDPP values. 
  Note that the red histogram has more mass towards the left, i.e., smaller values of CDPP, 
    indicating that our method overall outperforms PDC, the Kepler ``gold standard.'' 
}
\end{figure*}
